---
title: "HW2-Kalkunte"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo = FALSE}
library(tidyverse)
library(magrittr)
library(mosaic)
library(knitr)
library(kableExtra)

```

#Challenge 1
```{r}
d = read_csv("https://raw.githubusercontent.com/difiore/ada-2021-datasets/master/IMDB-movies.csv") #reading in data
head(d)

#pipe operation to create new d_filtered tibble that filters as desired
d %>% 
  filter(startYear>=1920 & startYear<=1979 & runtimeMinutes >= 60 & runtimeMinutes <= 180) %>% 
  mutate(decade = paste0(substr(startYear,3,3),"0s")) -> d_filtered
nrow(d_filtered)
ggplot(d_filtered, aes(x = runtimeMinutes)) + geom_histogram() + facet_wrap(vars(decade)) #plotting histograms of run minutes for each decade


d_filtered %>%
  group_by(decade) %>%
  summarize(mean = mean(runtimeMinutes),sd = sd(runtimeMinutes)) -> results

d_filtered %>%
  group_by(decade) %>%
  sample_n(100, replace = FALSE) %>%
  summarize(mean = mean(runtimeMinutes),sd = sd(runtimeMinutes)) -> sample_res
sample_res$se = sample_res$sd/10
results$se = results$sd/10
```

```{r}
results %>%
  kable("html", align = 'clc', caption = 'Results') %>%
    kable_styling(full_width = F, position = "left")
sample_res %>%
  kable("html", align = 'clc', caption = 'Results after Sampling') %>%
    kable_styling(full_width = F, position = "left")
```

COMPARE SMAPLE results to true results....print out table and compare in words the two

```{r}
reps = 1000
n = 100
for (i in names(table(d_filtered$decade))){
  subset = d_filtered[d_filtered$decade==i,]
  A = do(reps)*summarize(.data = sample_n(subset, size = n, replace = FALSE), mean = mean(runtimeMinutes),sd = sd(runtimeMinutes)) 
  assign(paste0(i,"_sampMean"),A)
  }
```

##Sampling Distributions
```{r}
#20s
('20sMean' = summarize(.data = `20s_sampMean`, mean = mean(`20s_sampMean`$mean), sd = sd(`20s_sampMean`$mean)))
hist(`20s_sampMean`$mean, main = "Histogram of 20s Sampling Distrubtion", xlab = "Mean runtime (min.)")
#30s
('30sMean' = summarize(.data = `30s_sampMean`, mean = mean(`30s_sampMean`$mean), sd = sd(`30s_sampMean`$mean)))
hist(`30s_sampMean`$mean, main = "Histogram of 30s Sampling Distrubtion", xlab = "Mean runtime (min.)")
#40s
('40sMean' = summarize(.data = `40s_sampMean`, mean = mean(`40s_sampMean`$mean), sd = sd(`40s_sampMean`$mean)))
hist(`40s_sampMean`$mean, main = "Histogram of 40s Sampling Distrubtion", xlab = "Mean runtime (min.)")
#50s
('50sMean' = summarize(.data = `50s_sampMean`, mean = mean(`50s_sampMean`$mean), sd = sd(`50s_sampMean`$mean)))
hist(`50s_sampMean`$mean, main = "Histogram of 50s Sampling Distrubtion", xlab = "Mean runtime (min.)")
#60s
('60sMean' = summarize(.data = `60s_sampMean`, mean = mean(`60s_sampMean`$mean), sd = sd(`60s_sampMean`$mean)))
hist(`60s_sampMean`$mean, main = "Histogram of 60s Sampling Distrubtion", xlab = "Mean runtime (min.)")
#70s
('70sMean' = summarize(.data = `70s_sampMean`, mean = mean(`70s_sampMean`$mean), sd = sd(`70s_sampMean`$mean)))
hist(`70s_sampMean`$mean, main = "Histogram of 70s Sampling Distrubtion", xlab = "Mean runtime (min.)")
```
Comment on shape of distributions

```{r}
samplingSE = c(`20sMean`$sd,`30sMean`$sd,`40sMean`$sd,`50sMean`$sd,`60sMean`$sd,`70sMean`$sd)
sErrors = cbind(results$se,sample_res$se,samplingSE)
rownames(sErrors) = names(table(d_filtered$decade))
colnames(sErrors) = c("True Population","100 Samples","Sampling Dist.")
sErrors
```
Comment on SEs - Sampling distribution looks to be fairly off...

#Challenge 2
```{r}
ppois(9, lambda=12)
ppois(0, lambda=12)
ppois(5, lambda=12)-ppois(4, lambda=12)
1-ppois(18, lambda=12)

x = 0:24
y = dpois(x, lambda=12) 
barplot(
  y,
  ylim = c(0, 0.5),
  names.arg = x,
  space = 0.1,
  xlab = "outcome",
  ylab = "Pr(X = outcome)",
  main = "Probability Mass Function"
)

Z = rpois(1460,12)
hist(Z,xlim = c(0,24))
```
How do your simulated results compare to the shape of the probability mass function you plotted above?

#Challenge 3
```{r}
d = read.csv("https://raw.githubusercontent.com/difiore/ada-2021-datasets/master/zombies.csv")
d_numeric = d[,c(5,6,7,8)]
n = nrow(d_numeric)
(m.POP = apply(d_numeric,2,mean))
(sd.POP = apply(d_numeric,2,sd)*sqrt((n-1)/n))
d_new = cbind(d_numeric,gender = d$gender)
```
##Boxplots
```{r}
ggplot(d,aes(x = factor(0), y = height)) + geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )+
  facet_grid(~gender)

ggplot(d,aes(x = factor(0), y = weight)) + geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )+
  facet_grid(~gender)

ggplot(d,aes(x = factor(0), y = zombies_killed)) + geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )+
  facet_grid(~gender)

ggplot(d,aes(x = factor(0), y = years_of_education)) + geom_boxplot(na.rm = TRUE, outlier.shape = NA) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )+
  facet_grid(~gender)
```
##Scaterplots
```{r}
ggplot(d,aes(x = age, y = weight)) + geom_point(aes(color =gender))
ggplot(d,aes(x = age, y = height)) + geom_point(aes(color =gender))
```
There seems to be a no relationship between weight and age,though males look to have a higher average weight than females at all ages. There seems to be a positive relationship between age and height with again a higher mean height for males at any age vs females.

##Normal Distribution
```{r}

```



